%! Author = Philipp Emmenegger
%! Date = 09/07/2021

\section{Introduction SPA}
\subsection{Browser-based Applications}
\textbf{Benefits:} Platform independent, including mobile,
No software update, no application, easy maintenance, 
Software can be provided as a service (SaaS - pay as you go),
Code separation\\
\textbf{Liabilities:} No data sovereignty (Datenhoheit),
Limited/restricted hardware access,
SEO - Search engines must execute JavaScript,
More complex deployment strategies

\subsection{SPA}
Fits on a single web page, user experience of a desktop application.
All code is retrieved with a single page load or resources are dynamically loaded.
AJAX and HTML5 to create responsive Web apps, without constant page reloads.

\subsubsection{Bundling}
Code delivered over potentially slow networks.
Bundling and minifying the source leads to smaller SPA footprint.
Larger SPAs with many modules need dependency management.
Initial Footprint reduced by loading dependent modules on-demand.

\subsubsection{WebPack as Bundler}
\textbf{Entry:} Start, follows the graph of dependencies to know what to bundle.
\textbf{Output:} Tell webpack where to bundle your application.
\textbf{Loaders:} Transforms these files into modules as they are added to your dependency graph.
\textbf{Plugins:} Perform tasks like bundle optimization, asset management and injection of env variables.
\textbf{Mode:} Enable built-in optimization mechanisms.

\subsection{Routing}
Completely on client-side by JS. 
Navigation behaves as usual.
Browser needs to fake the URL to change and store page state.
\textit{window.history.pushState}.

\subsection{Dependency Injection}
Reduces coupling between consumer and implementation.
Contracts between classes are based on interfaces.
Supports the open/closed principle.
Allows flexible replacement of an implementation.

\subsubsection{Decorators}
Provide a way to add annotations / meta-programming syntax.
Can be attached to a class declaration, method, accessor, property or parameter.
Widely used in Angular.